The K2 Bright Star Survey I: Methodology and Data Release

### 2019-07-03 paper/ms.tex
lightkurve in software

\software{\textsc{k2sc} \citep{Aigrain2015,k2sc}; IPython  \citep{PER-GRA:2007}; SciPy \citep{scipy}; and Astropy, a community-developed core Python package for Astronomy \citep{astropy}.}

>>>>

\software{\textsc{k2sc} \citep{Aigrain2015,k2sc}; \texttt{lightkurve} \citep{lightkurve}; IPython \citep{PER-GRA:2007}; SciPy \citep{scipy}; and Astropy, a community-developed core Python package for Astronomy \citep{astropy}.}
